NFC and burnout in teachers - A replication and extension study

### 2022-07-20 Manuscript/Revision_Letter.Rmd
Update Revision Letter

This is our response

\Assignment{First Author}
\WorkInProgress
\Easy

@@

\Assignment{Which Author?}
\AlmostDone
\Medium

@@

This is our response

\Assignment{First Author}
\WorkInProgress
\TimeConsuming
\Hard
\NotEstimated

@@

\RC{p.21 “The mediator that did not reach significance was the perception of own resources exceeding the job demands. As this latent variable was conceptualized as boredom at work, we could not confirm the positive association of boredom and burnout found by Reijseger et al. (2013.)”

@@

@@

\Assignment{First or Last Author}
\WorkInProgress

@@

We like to thank the reviewer very much for this positive assessment of our manuscript. In our revision, we now provide a reliability estimate (in terms of Cronbach's $\alpha$) of the scale used to assess Covid-19 burden, see p.XX.

>>>>

\Assignment{JZ}
\WorkInProgress
\Easy

@@

\Assignment{JZ}
\AlmostDone
\Medium

@@

We acknowledge that this sentence was unfortunate. We changed it accordingly and now write in the abstract:

> While there is evidence that certain personality traits promote or protect against burnout, the role of dispositional cognitive motivation has been investigated only recently.

\Assignment{AS}
\Done

@@

\Assignment{JZ}
\WorkInProgress
\Easy

\RC{p. 21 “The mediator that did not reach significance was the perception of own resources exceeding the job demands. As this latent variable was conceptualized as boredom at work, we could not confirm the positive association of boredom and burnout found by Reijseger et al. (2013.)”

@@

\Assignment{JZ}
\WorkInProgress
\Easy

@@

\Assignment{JZ}
\WorkInProgress
\Easy

@@

We like to thank the reviewer very much for this positive assessment of our manuscript. In our revision, we now provide a reliability estimate (in terms of Cronbach's $\alpha$) of the scale used to assess Covid-19 burden, see p. XX.
